### 2019-10-07 proposal/figures/mod_train.tex
Initial commit

  \node[draw, minimum height=1cm,minimum width=3cm] at (0, 3) (n_1)             {Initial System};
  \node[draw, minimum height=1cm,minimum width=3cm, pattern=north west lines, pattern color=blue!20!white] (n_2) [below=0.75cm of n_1] {Fluid parameters};
  \node[draw, minimum height=1cm,minimum width=3cm, pattern=north west lines, pattern color=blue!20!white] (n_3) [below=0.75cm of n_2] {Inflow speed};
  \node[draw, minimum height=1cm,minimum width=3cm, pattern=north west lines, pattern color=blue!20!white] (n_4) [below=0.75cm of n_3] {Object in space};

  \draw [->, shorten >=3pt, shorten <=3pt, thick ] (n_1) edge (n_2);
  \draw [->, shorten >=3pt, shorten <=3pt, thick ] (n_2) edge (n_3);
  \draw [->, shorten >=3pt, shorten <=3pt, thick ] (n_3) edge (n_4);

\end{tikzpicture}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

>>>>

  \node[draw, minimum height=1cm,minimum width=4cm] at (0, 3) (mod)             {Modifications};
  \node[draw, minimum height=1cm,minimum width=4cm] (train) [below=1cm of mod] {Training \& Evaluating};

  \draw [->, thick] (mod.east) to [out = 0, in = 0, looseness = 2] (train.east);
  \draw [->, thick] (train.west) to [out = 180, in = 180, looseness = 2] (mod.west);

\end{tikzpicture}
\end{document}
